%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  New template code for TAMU Theses and Dissertations starting Fall 2016.  
%
%
%  Author: Thesis Office
%  
%  Last Updated: 1/13/2021
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                           ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{ACKNOWLEDGMENTS}
\addcontentsline{toc}{chapter}{ACKNOWLEDGMENTS}  % Needs to be set to part, so the TOC doesnt add 'CHAPTER ' prefix in the TOC.

Many people lent me their support during the development of this dissertation, and I am very happy to acknowledge them here. My sincere thanks go to my research advisors, Dr. Daniel Berleant and Dr. Maria Gingras. Both took an interest in me and helped shape my ideas for this research. 

Dr. Berleant has been an instructor to me since the days of my undergraduate degree. I am glad to have had the opportunity to perform my first, rigorous research project under a professional of his calibur.

Dr. Gingras (Maria) is both a professional and personal mentor to me, and I am thankful that she lent her time to become an affiliate faculty member of UA Little Rock and join my dissertation committee. Maria is a wealth of knowledge in the market monitoring discipline, and her instruction, mentorship, and encouragement have made a tremendous difference in my life.

My thanks also goes to the other members of my dissertation committee, Dr. Elizabeth Pierce and Dr. Ningning Wu. Your guidance throughout my academic career has been nothing short of a blessing. I also must thank Dr. John Talburt, whom encouraged me to join the information quality program at UA Little Rock many years ago. 

Finally, I want to acknowledge the contributions of my co-workers and friends within the market monitoring unit at Southwest Power Pool. Many of my colleagues in the MMU have lent their expertise to help me succeed in my work, and I couldn't have completed my dissertation without their support. Special thanks go to both my best friend and colleague, Mark Rouse, and my manager, Raleigh Mohr. Mark has been a steadfast friend in my career, and Raleigh has been an incredibly supportive mentor. I am thankful to acknowledge their help as I completed this program.

\pagebreak{}