%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  New template code for TAMU Theses and Dissertations starting Spring 2021.  
%
%
%  Author: Thesis Office
%  
%  Last Updated: 1/13/2021
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                           DEDICATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{DEDICATION}
\addcontentsline{toc}{chapter}{DEDICATION}  % Needs to be set to part, so the TOC doesnt add 'CHAPTER ' prefix in the TOC.

\begin{center}
\vspace*{\fill}
\noindent \textit{I attempted suicide, in 2022, in the wake of a devastating personal event. I am thankful that it was an attempt that ended in failure. For my true friends Jacob and Meredith Tillman (née Ashley), you will always have my gratitude for saving my life.}

\vspace*{\fill}

\noindent \textit{If I can name one thing that pulled me through the years following that experience, it would be my family. It would constitute an absurd lack of devotion on my part to dedicate this dissertation to anyone other than them. My parents have shown my siblings and I nothing but love in our lives. For as much as I earned this achievement, I earned it to share with the Grasby family.}

\vspace*{\fill}

\noindent \textit{For my parents, Tina and Charles. For my sister, Madasyn. For my brother and sister-in-law, Robert, Brittany (and my nephews, Miles and Maddox). For my cousin, David Parker. For my grandmother, Louise. For my late grandparents, Hubert and Addie Mae. For my maternal, late, grandfather that I never got the chance to meet, Desi Sandoval. For my paternal uncle, Leonard. And for a true family friend that died too young, Doug Durham. I am glad that I am still here to share this life with each of you. Any benefit that this research brings to society: I dedicate to you.}

\vspace*{\fill}

\noindent \textit{Furthermore, I want to extend the family metaphor. For anyone that reads this- any human- that has struggled with their mental health, their identity, or finding their place in the world: I understand. I have been there. We are all in this together. This achievement is for you, too.}

\vspace*{\fill}

\noindent \textit{And, finally, to both Miss Natasha and Rebecca- thank you, both, for changing my life (albeit in fundamentally different ways).}
\end{center}

\pagebreak{}